Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha line emission

### 2016-05-26 paper/letter.tex
size correction

A future observational test of this possibility in \tol\ would require
integral field unit measurements spatially resolving its spatial
extent. 
\tol\ spans a region of $4$ arcminutes. 
An instrument such as the Multi Unit Spectroscopic Explorer with its
nominal $0.2$ arcseconds spatial sampling over a $1.0$ arcminute field
in wide-field mode could provide a detailed mapping of different
ionization lines to infer a kinematic map.

@@

The optical emission  comes from a   region with approximate diameter
?? \cite{Fricke01}.

>>>>

A future observational test of this possibility in \tol\ would require
integral field unit measurements spatially resolving its spatial
extent. 
\tol\ spans a region of $4$ arcseconds. 
An instrument such as the Multi Unit Spectroscopic Explorer with its
nominal $0.2$ arcseconds spatial sampling over a $1.0$ arcminute field
in wide-field mode could provide a coarse mapping of different
ionization lines to infer a kinematic map.

@@

The optical emission  comes from a   region with approximate diameter
4 kpc \cite{Fricke01}.
